---
title: "Analysis on the Relations between Subjective Class and Objective family Income Status"
date: "2014.10.21"
author: "Han-Wool Jeong"
output:
  html_document:
    theme: cerulean
---

<!-- For more info on RMarkdown see http://rmarkdown.rstudio.com/ -->

<!-- Enter the code required to load your data in the space below. The data will be loaded but the line of code won't show up in your write up (echo=FALSE) in order to save space-->
```{r echo=FALSE}
load(url("http://bit.ly/dasi_gss_data"))
```

<!-- In the remainder of the document, add R code chunks as needed -->

### Introduction:

This analysis is to verify if subjective class identification represents objective class status correctly by using "General Social Survey Cumulative File, 1972-2012 Coursera Extract." My hyperthesis is that there is a difference between the average of respondent's family income from self reported classes.

To compare means of 3+ groups, I use a test called analsys of variance(ANOVA) and F statisic.

H0: M1 =M2 = ... Mk 
HA: At least one pair of means are different from each other. 


### Data:
(1) Description

- variable y <- gss$coninc (numeric variable)
```{r}
summary(gss$coninc)
boxplot(gss$coninc)
```

- variable x <- gss$class
```{r}
table(gss$class)
barplot(table(gss$class))

```

Insert data section here...

### Exploratory data analysis:

-Data Cleaning
```{r}
y <- gss$coninc
x <- gss$class
x_clean <- x[x != "No Class"] # excluding "No Class"
droplevels(x_clean)
```

- loading inference # function
```{r}
source("http://bit.ly/dasi_inference")
```

- ANOVA Test
```{r}
inference(y, x_clean, est="mean", type="ht",alternative="greater", method="theoretical")

```

### Inference:

- p-value is the probability of at least as large a ratio between the "between" and "within" group variabilities if in fact the means of all groups are equal.
- According to the results from ANOVA test, p-value is very small and less than alpa, reject Ho. 
- The Data provides convincing evidence that at least one pair of population means of family income are different from selp reported class

### Conclusion:

For American adults, the variable of "subjective class" is a valid indicator to represent the difference in the objective income status. 
